\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc} % Make sure the font is rendered nicely
\usepackage{enumitem} % list indentation
\usepackage[margin=2cm,centering=true]{geometry}
\usepackage{graphicx} % For \cs
\usepackage{datetime} % Custom date format
\usepackage{tabularx}
\usepackage{titlesec} % titleformat/section lines

% Custom commands
\newcommand{\cpp}{C{}\texttt{++}}
\newcommand{\cs}{\settoheight{\dimen0}{C}C\kern-.05em \resizebox{!}{\dimen0}{\raisebox{\depth}{\textbf{\#}}}}
\renewcommand{\arraystretch}{1.5}

\def\myemail{charles@pigott.org.uk}
\def\myphone{07821 169013}

\newdateformat{mydate}{\monthname[\THEMONTH] \THEYEAR}

% tabularx
\newcolumntype{L}{>{\scshape\raggedleft}p{3.5cm}}
\newcolumntype{R}{>{}X}

\newenvironment{myitemize}
{\begin{itemize}[leftmargin=.75in,rightmargin=.75in]
  \itemsep1pt \parskip0pt \parsep0pt}
{\end{itemize}}

\titleformat{\section}{\Huge\scshape\raggedright}{}{0em}{}[\titlerule]

\begin{document}
\pagenumbering{gobble} % disable page numbers

% "title" & info
\noindent\begin{minipage}{0.4\textwidth}
\textbf{\Huge{Charles Pigott}}
\end{minipage}
\hfill
\begin{minipage}{0.4\textwidth}
\begin{flushright}
  \texttt{\myemail}\\
  \myphone\\
\end{flushright}
\end{minipage}

\par

\section{Profile}
I am currently in my final year of studying Computer Science and Mathematics at
the University of York. I already have a year of professional experience in an
IT-related role. Available from July 2017 full-time.

\section{Experience}
\noindent\begin{tabularx}{\textwidth}{@{}L R@{}}
  July~2015 --- September~2016 &
  \textbf{Systems Administrator} \par
  \textit{Bytemark Hosting}
\end{tabularx}
\begin{myitemize}
  \item 15 month industrial placement, as part of university course.
  \item Time split between technical support and software development.
  \item Technical support role was largely Linux based, and involved
    communicating directly with customers via `phone \& email.
  \item Significant experience with domains, networking (including LINX
    Networking course) and webserver maintenance.
  \item Out-of-hours support on a rota, approximately one week per month.
  \item Development work maintaining a Ruby-on-Rails web application responsible
    for mapping Bytemark's IP address space.
  \item Additional development work in Go \& Python.
  \item Occasional physical work running cables and building servers in the
    data centre.
\end{myitemize}

\noindent\begin{tabularx}{\textwidth}{@{}L R@{}}
  October~2013 --- Present &
  \textbf{Head of Computing} \par
  \textit{University Radio York}
\end{tabularx}
\begin{myitemize}
  \item Volunteered for the Computing Team at URY shortly after starting
    University.
  \item Software development spread across various languages.
  \item System administration spread across FreeBSD, Debian \& Windows systems.
  \item Database administration experience with PostgreSQL\@.
  \item Various leadership roles, including Assistant Head of Computing for
    2014/15 year, and Head of Computing in 2016.
  \item Currently responsible for managing other members of Computing Team and
    maintaining the uptime of the radio station on a limited budget.
\end{myitemize}

\section{Technical Skills}
\begin{myitemize}
  \item Skilled at C, \cpp, HTML \& CSS, Python, PHP, Bash, Go, SQL and \LaTeX{}
    languages.
  \item Experience with many others, including Java, JavaScript (incl.\ jQuery),
    \cs{}, Ruby and Rust.
  \item Highly practiced with Version control systems such as Git and
    Subversion.
  \item 8 years of Linux desktop \& server usage in development and system
    administration contexts.
\end{myitemize}

\section{Education}
\noindent\begin{tabularx}{\textwidth}{@{}L R@{}}
  Autumn~2013 --- Present &
  \textbf{University of York, UK}
\end{tabularx}
\begin{myitemize}
  \item BSc Computer Science \& Mathematics (expected 2:1)
  \item Final year thesis titled \textit{``Binary Code Translation from
    Register to Stack based code''}
  \item Notable module results include \textit{``Theory and Practice of
    Programming Languages''} --- 74\% \& \textit{``Principles of Programming
    Languages''} --- 75\%
\end{myitemize}

\noindent\begin{tabularx}{\textwidth}{@{}L R@{}}
  Autumn~2008 --- Summer~2013 &
  \textbf{Hartismere School, Eye, Suffolk, UK} \par
\end{tabularx}
\begin{myitemize}
  \item A-levels in Physics~(A), Mathematics~(A), Further~Mathematics~(B)
\& Computing~(B); AS level in Chemistry~(B)
  \item 11 GCSEs (Maths, Physics, Chemistry, %A*
    Biology, History, %A
    Music, Geography, English, %B
    R.E., French, English Literature) %3C
\end{myitemize}

\section{Other Interests}
\begin{myitemize}
  \item Development work for several open-source projects, usually in
    \cpp~(notably OpenTTD and FreeRCT, reimplementations of old games). Other
    personal development work can be found at \texttt{github.com/LordAro}.
  \item ``Infrastructure officer'' of HackSoc (UoY's computer science society)
    and responsible since 2014 for maintaining their Linux servers.
  \item Leisure interests include reading and music (having achieved
    Grades 7, 6 \& 6 on Violin, Piano \& Trombone respectively).
  \item Keen cyclist (also used for commuting to work during placement year).
  \item Learning to drive, test booked for March.
\end{myitemize}

\noindent{}References available on request.

\end{document}
